Cultural Transmission and Technological Transitions during the Late Paleolithic in Korea

### 2022-10-10 analysis/paper/paper.qmd
test table caption

```{r}
#| label: tab-landmark-abbreviations

here::here("analysis/data/raw_data/table-of-landmark-abbreviations.csv") %>% 
  read_csv() %>% 
  knitr::kable(., caption = "Description of artefact landmarks used in this study")

@@

```{r}
#| label: tab-cv-over-time

@@

# apply t test to each variable
# prepare df for t test : ML
t_test_df_ML_2<- 
df_sitename %>%
  dplyr::select(-sitename, -SPstage.Raw_material) %>%
  group_by(SPstage.Stage) %>%
  add_tally() %>%
  dplyr::filter(SPstage.Stage > 1)%>%
  dplyr::select(-n) %>% 
   pivot_longer(-SPstage.Stage,
               names_to = "variable",
               values_to = "value") %>% 
  filter(variable == "ML", SPstage.Stage == 2)

t_test_df_ML_3<- 
df_sitename %>%
  dplyr::select(-sitename, -SPstage.Raw_material) %>%
  group_by(SPstage.Stage) %>%
  add_tally() %>%
  dplyr::filter(SPstage.Stage > 1)%>%
  dplyr::select(-n) %>% 
   pivot_longer(-SPstage.Stage,
               names_to = "variable",
               values_to = "value") %>% 
  filter(variable == "ML", SPstage.Stage == 3)

t.test(t_test_df_ML_2$value, t_test_df_ML_3$value)
#t = 3.7637, df = 135.36, p-value = 0.0002485

>>>>

```{r}
#| label: tbl-landmark-abbreviations
#| tbl-cap: Description of artefact landmarks used in this study

here::here("analysis/data/raw_data/table-of-landmark-abbreviations.csv") %>% 
  read.csv() %>% 
  knitr::kable(.)

```
@tbl-landmark-abbreviations sth special~

@@

```{r}
#| label: tbl-cv-over-time

@@

```
@tbl-cv-over-time says sth interesting
